\documentclass{article}
\title{engDevTools Documentation}
\date{Started: 05-24-2018}
\author{Kevin Gomez}

\begin{document}
	
	\pagenumbering{gobble}
	\maketitle
	\newpage
	\pagenumbering{arabic}
	
	\section{Architecture Overview}
	
	\section{Function Types}
		\begin{enumerate}
			\item MEM: Functions dealing with handling memory allocation and access.
			\item SET: Functions for initializing or setting data.
			\item CHECK: Functions for checking properties of data.
			\item OPS: Functions that conduct arithmetic operations.
			\item FREE: Functions that free memory.
			\item PRINT: Functions that conduct printing operations.
			\item READ: Functions that conduct reading operations.
			\item WRITE: Functions that conduct writing operations.
		\end{enumerate}
	
	\section{Base Modules}
		\subsection{vmaOps (math)}
			\subsubsection{vectorOps}
				Status: In Development \newline
				Purpose: Handle vector operations \newline
				Capability:
				\begin{enumerate}
					\item Vector Arithmetic
					\begin{enumerate}
						\item Vector Addition
						\item Vector Subtraction
					\end{enumerate}
					\item Vector Operations
					\begin{enumerate}
						\item Cross Product
						\item Dot Product
						\item Unit Vector
						\item Vector Magnitude
					\end{enumerate}
				\end{enumerate}
				
			\subsubsection{matrixOps}
				Status: In Development \newline
				Purpose: Handle 3x3 matrix operations \newline
				Capability: 
				\begin{enumerate}
					\item Initialization/Freeing
					\begin{enumerate}
						\item Matrix Initialization
					\end{enumerate}
					\item Set Matrix
					\begin{enumerate}
						\item Zeros Matrix
						\item Ones Matrix
						\item Identity Matrix
					\end{enumerate}
					\item Matrix Arithmetic
					\begin{enumerate}
						\item Matrix Addition
						\item Matrix Subtraction
						\item Matrix Multiplication
						\item Scalar * Matrix
					\end{enumerate}
					\item Matrix Operations
					\begin{enumerate}
						\item Matrix Trace
						\item Matrix Determinant
						\item Matrix Transpose
					\end{enumerate}
					\item Matrix Checks
					\begin{enumerate}
						\item Matrix isEqual
					\end{enumerate}
				\end{enumerate}
			\subsubsection{arrayOps}
				Status: In Development \newline
				Purpose: Handle nxn matrix operations \newline
				Capability: 
				\begin{enumerate}
				\item Initialization/Freeing
				\begin{enumerate}
					\item Array Initialization
					\item Array Free
				\end{enumerate}
				\item Set Array
				\begin{enumerate}
					\item Zeros Array
					\item Ones Array
					\item Identity Array
				\end{enumerate}
				\item Array Arithmetic
				\begin{enumerate}
					\item Array Addition
					\item Array Subtraction
					\item Array Multiplication
					\item Scalar * Array
				\end{enumerate}
				\item Array Operations
				\begin{enumerate}
					\item Array Transpose
				\end{enumerate}
				\item Array Checks
				\begin{enumerate}
					\item Array isEqual
				\end{enumerate}
				\item Miscellaneous
				\begin{enumerate}
					\item 2x2 Determinant
				\end{enumerate}
			\end{enumerate}
			\subsubsection{printOps}
				Status: In Development
				Purpose: Basic printing capability
				Capability:
				\begin{enumerate}
					\item Printing Variables
					\begin{enumerate}
						\item Print Boolean
						\item Print Scalar
						\item Print Vector
						\item Print Matrix
						\item Print Array
					\end{enumerate}
				\end{enumerate}
			\subsubsection{writeOps}
				Status: Not Started
			\subsubsection{readOps}
				Status: Not Started	

	\section{Basic Simulation Modules}
		\subsection{Modules}
			\subsubsection{Astrodynamics}
				Status: Not Started
			\subsubsection{Electronics}
				Status: Not Started
			\subsubsection{Thermodynamics}
				Status: Not Started
			\subsubsection{Aerodynamics}
				Status: Not Started
			\subsubsection{Mass Properties}
				Status: Not Started
			
	\section{Advanced Simulation Modules}

\begin{enumerate}
	\item Hello!
\end{enumerate}	

	\section{User Interface}

\begin{enumerate}
	\item Hello!
\end{enumerate}	

	\section{Unit/Regression Testing}

\begin{enumerate}
	\item Hello!
\end{enumerate}	

	\section{Data Pre-processing}

\begin{enumerate}
	\item Hello!
\end{enumerate}	

	\section{Data Post-processing}

\begin{enumerate}
	\item Hello!
\end{enumerate}	

	\section{Support Functions/Scripts}

\begin{enumerate}
	\item Hello!
\end{enumerate}	

\end{document}